Characterization of an anionic membrane mimetic with natural phospholipid content and magnetic orienting capabilities

### 2020-09-02 article.tex
Correcciones al manuscrito terminadas

	Another condition that the mimetic must fulfill, is that the mimetic must
  orient itself in presence of an external magnetic field. This is so the
  deuterated probes in the mimetic can produce a \textit{quadrupole splitting}
  in a solution $^2$H-RMN spectrum, which will be used to calibrate the MD
  simulations. This calibrated simulation can be used to assess other
  properties, not possible to measure experimentally, with more
	confidence.\\

@@

	In order to obtain more reliable information from a molecular dynamic
	simulation,
	it is desirable that experimentally measured properties are well reproduced by
	calculations. That said, MD has to be calibrated to reproduce known experimental
	results, which is why
	we
	tested multiple force-fields to see which one yields a closer representation of
	the aliphatic chain dynamics, evidenced by reproducing $^2$H-RMN quadrupole
	splittings. Figure \ref{fig:reference} shows the $^2$H-NMR spectrum of the
	membrane mimetic prepared according to the composition stated in table
	\ref{tab:mimetic_composition}, enriched with \ce{H2O}(0.5\% of the total
	\ce{H2O} replaced by \ce{D2O}) and SDS-d$_{25}$(10\% of the total SDS replaced
	by SDS-d$_{25}$). The quadrupolar splitting of each C-D bond depends largely on
	their order parameter ($S_{CD}$, see equation \ref{eq:splitting}), therefore it
	makes sense to assign each quadrupolar splitting from the least ordered to the
	most ordered methylene, resulting as follows: The central signal arises from an
	average in time of HDO oriented at the interface in fast exchange with
	non-oriented HDO at the bulk (smallest splitting, \SI{388}{Hz}. Not shown). The
	next less split signal arises from the deuterated methyl group (\ce{CD3}-)
	capping the tail of each SDS-d$_{25}$, as the rotation of this group produces a
	lower order parameter, the smallest along the chain. The rest of the more split
	signals correspond to subsequent deuretated methylenes (-\ce{CD2}-), with the
	ones closer to the charged sulphate head-group having a higher quadrupolar
	splitting, since the strong Coulombic interaction between this charged end and
	the interface produces a restraining effect on the movement of the nearby
	deuterons. The adjustment of the simulation relies on the accurate reproduction
	of these quadrupolar splittings from SDS-d$_{25}$, as they reflect the dynamics
	of the lipid chains in the bilayer.\par
	\begin{figure}[h]
		\centering
		\includegraphics[width=\columnwidth]{nmr_reference}
		\caption{$^2$H-NMR spectrum of membrane mimetic enriched with SDS-d$_{25}$.
			Central peak (not shown completely) belongs to \ce{HDO} present in the
			sample, while the rest of the signals are split SDS-d$_{25}$ signals which
			were used as reference to calibrate a computational model.}
		\label{fig:reference}
	\end{figure}
	Initially,
	three force-fields with different partial charge distributions were tested.
	These force-fields were chosen due to their ability to reproduce other
	structures of
	SDS aggregates\cite{Tang2014}.\par
	The tested force-fields were:
	\begin{itemize}
		\item CHARMM36\cite{Vanommeslaeghe2009}
		\item Berger\cite{Berger1997} with partial charge distribution according to
		Merz-Kollman
		method\cite{Besler1990}
		\item Berger with partial charge distribution according to
		Gromos53A6\cite{Oostenbrink2004}
		parameters.
		\item Gromos53A6 with partial charge distribution according to Merz-Kollman
		method.
		\item Gromos53A6 with partial charge distribution according to its own
		parameters.
	\end{itemize}

@@

	Polarized light microscopy of the mesophase shows a thread-like pattern, this
	is
	characteristic of a lyotropic nematic phase\cite{dierking2006textures}.
	Furthermore, considering the magnitude of the measured quadrupolar
	splittings, and the fact that each methylene's deuteron pair in SDS-d$_{25}$
	yields
	a
	single quadrupolar splitting in solution $^2$H-NMR (see figure
	\ref{fig:reference}), we can conclude that this phase has a bilayer
	like structure with its bilayer normal perpendicular
	to the magnetic field ($\theta=\pi/2$ in eq. \ref{eq:splitting}). The
	posibility of a calamitic phase is discarded, since a calamitic phase implies a
	director axis being parallel to the magnetic field ($\theta=0$ in eq.
	\ref{eq:splitting}) which would produce splittings considerably smaller than
	observed. Regarding the size of the aggregate, cryo-TEM imagery of similar
  bicelles (made with TTA\footnote{Trimethyltetradecylammonium} instead of SDS)
  results in aggregates of about
  \SI{2}{nm}-\SI{5}{nm}\todo{RSCAdv.,2016,6,7455}, and we expect for the size of
  the membrane mimetic aggregate to be in the same order of magnitude.\\

>>>>

	Another condition that the mimetic must fulfill, is that the magnetic susceptibility of the mesophase of the mimetic must be anisotropic so it can orient itself when exposed to an external magnetic field. This is so the
  deuterated probes in the mimetic can produce a \textit{quadrupole splitting}
  in a solution $^2$H-RMN spectrum, which will be used to calibrate the MD
  simulations. This calibrated simulation can be used to assess other
  properties, not possible to measure experimentally, with more
	confidence.\\

@@

	In order to obtain more reliable information from a molecular dynamic
	simulation,
	it is desirable that experimentally measured properties are well reproduced by
	calculations. That said, MD has to be calibrated to reproduce known experimental
	results, which is why
	we
	tested multiple force-fields to see which one yields a closer representation of
	the aliphatic chain dynamics, evidenced by reproducing $^2$H-RMN quadrupole
	splittings. Figure \ref{fig:reference}-A shows the $^2$H-NMR spectrum of the
	membrane mimetic prepared according to the composition stated in table
	\ref{tab:mimetic_composition}, enriched with \ce{D2O}(0.5\% of the total
	\ce{H2O} replaced by \ce{D2O}) and SDS-d$_{25}$(10\% of the total SDS replaced
	by SDS-d$_{25}$). The quadrupolar splitting of each C-D bond depends largely on
	their order parameter ($S_{CD}$, see equation \ref{eq:splitting}), therefore it
	makes sense to assign each quadrupolar splitting from the least ordered to the
	most ordered methylene, resulting as follows: The central signal arises from an
	average in time of HDO oriented at the interface in fast exchange with
	non-oriented HDO at the bulk (smallest splitting, \SI{388}{Hz}. Not shown). The
	next less split signal arises from the deuterated methyl group (\ce{CD3}-)
	capping the tail of each SDS-d$_{25}$, as the rotation of this group produces a
	lower order parameter, the smallest along the chain. The rest of the more split
	signals correspond to subsequent deuretated methylenes (-\ce{CD2}-), with the
	ones closer to the charged sulphate head-group having a higher quadrupolar
	splitting, since the strong Coulombic interaction between this charged end and
	the interface produces a restraining effect on the movement of the nearby
	deuterons. The adjustment of the simulation relies on the accurate reproduction
	of these quadrupolar splittings from SDS-d$_{25}$, as they reflect the dynamics
	of the lipid chains in the bilayer.\par
	\begin{figure}[h]
		\centering
		\includegraphics[width=\columnwidth]{nmr_reference.pdf}
		\caption{$^2$H-NMR spectrum of: (A) membrane mimetic enriched with SDS-d$_{25}$.
			Central peak (not shown completely) belongs to \ce{HDO} present in the
			sample, while the rest of the signals are split SDS-d$_{25}$ signals which
			were used as reference to calibrate a computational model. (B) DMPC/DHPC bicelle with added cholesterol and polyinsaturated phospholipids and enriched with DMPC-d$_{54}$ (R.E. Minto \textit{et al.}, Chem. Phys. Lipids 132 (2004) 55–64)}
		\label{fig:reference}
	\end{figure}
	Initially,
	three force-fields with different partial charge distributions were tested.
	These force-fields were chosen due to their ability to reproduce other
	structures of
	SDS aggregates\cite{Tang2014}.\par
	The tested force-fields were:
	\begin{itemize}
		\item CHARMM36\cite{Vanommeslaeghe2009}
		\item Berger\cite{Berger1997} with partial charge distribution according to
		Merz-Kollman
		method\cite{Besler1990}
		\item Berger with partial charge distribution according to
		Gromos53A6\cite{Oostenbrink2004}
		parameters.
		\item Gromos53A6 with partial charge distribution according to Merz-Kollman
		method.
		\item Gromos53A6 with partial charge distribution according to its own
		parameters.
	\end{itemize}

@@

	Polarized light microscopy of the mesophase shows a thread-like pattern, this
	is
	characteristic of a lyotropic nematic phase\cite{dierking2006textures}.
	Furthermore, considering the magnitude of the measured quadrupolar
	splittings, and the fact that each methylene's deuteron pair in SDS-d$_{25}$
	yields
	a
	single quadrupolar splitting in solution $^2$H-NMR (see figure
	\ref{fig:reference}-A), we can conclude that this phase has a bilayer
	like structure with its bilayer normal perpendicular
	to the magnetic field ($\theta=\pi/2$ in eq. \ref{eq:splitting}). The
	posibility of a calamitic phase is discarded, since a calamitic phase implies a
	director axis being parallel to the magnetic field ($\theta=0$ in eq.
	\ref{eq:splitting}) which would produce splittings considerably smaller than
	observed. Regarding the size of the aggregate, cryo-TEM imagery of similar
  bicelles (made with TTA\footnote{Trimethyltetradecylammonium} instead of SDS)
  results in aggregates of about
  \SI{2}{nm}-\SI{5}{nm}\todo{RSCAdv.,2016,6,7455}, and we expect for the size of
  the membrane mimetic aggregate to be in the same order of magnitude.\\
   When comparing the NMR spectrum of this bicelle (figure \ref{fig:reference}-A) with one taken from a DHPC/DMPC bicelle with cholesterol and polyinstaturated phospholipids (figure \ref{fig:reference}-B)\todo{R.E. Minto \textit{et al.}, Chem. Phys. Lipids 132 (2004) 55–64}, one can see that DMPC-d$_{54}$ splittings (and hence order parameters) are similar to the splittings in SDS-d$_{25}$, therefore one can conclude that the orientational dynamics of this SDS-containing mimetic are similar to a mimetic made from purely phospholipid.\\

### 2020-09-02 revision_cover_letter.tex
Correcciones al manuscrito terminadas

\documentclass{letter}
\usepackage{siunitx}

@@

  Regarding the observations both of the reviewers, we have made multiple changes to
  our manuscript in order to amend the issues found by the reviewers, as
  follows:

@@

@@

  \item Reviewer 2 said: \textit{A discussion involving the comparison of the order parameters of the present model with the order parameters from natural phospholipidic membranes is necessary.}\\

 \end{itemize}

>>>>

\documentclass{letter}
\usepackage{siunitx}
\usepackage[letterpaper,lmargin=3cm,rmargin=3cm]{geometry}

@@

  Regarding the observations both of the reviewers, we have made multiple changes to
  our manuscript in order to amend the issues found by them, they are listed as
  follows:

@@

\item Reviewer 1 said: \textit{By the same reasoning, the orientation of bicelles reflect their size / anisotropy in the NMR time scale. It is not that “it orient ifself” as stated here: “Also, the membrane mimetic must orient itself in presence of an external magnetic field. This is so the deuterated probes in the mimetic can produce a quadrupole splitting in a solution 2H-RMN spectrum”. Please rephrase that.}
We agree, the preferred orientation of the bicelle is the result of the anisotropy of its magnetic susceptibility. The sentence has been modified to reflect that.

@@

  \item Reviewer 1 said: \textit{What about the calculated order parameters? If they were calculated, why not to compare them with the literature?}. Reviewer 2 had a similar concern, and said: \textit{A discussion involving the comparison of the order parameters of the present model with the order parameters from natural phospholipidic membranes is necessary.}\\
  We agree. A comparison between quadrupolar splittings (and hence order parameters) of our proposed membrane mimetic and a DHPC/DMPC bicelle with added cholesterol and polyinsaturated phospholipids has been included, and it reads: "\textit{When comparing the NMR spectrum of this bicelle (figure 4-A) with one taken from a DHPC/DMPC bicelle with cholesterol and polyinstaturated phospholipids (figure 4-B), one can see that DMPC-d$_{54}$ splittings (and hence order parameters) are similar to the splittings in SDS-d$_{25}$, therefore one can conclude that the orientational dynamics of this SDS-containing mimetic are similar to a mimetic made from purely phospholipid}"

	\item Regarding the language issues pointed by Reviewer 1, we have revisioned the manuscript and the Highlights file, and fixed a number of typographic errors.
 \end{itemize}
